### 2013-02-07 doc/icml2013/intro.tex
Updated the outline for the paper

Local optima are a common problem faced when learning parameters in
latent variable models. Recently, there has been an interest in spectral
algorithms that provide statistically consistent estimators, i.e. given
sufficient data they are guaranteed to converge to the global optimum,
given that the model is identifiable. Furthermore, these algorithms have
polynomial sample and computational complexities for several such
models, e.g.  hidden Markov models \cite{anandkumar-hsu-kakade2012},
probabilistic context free grammars \cite{hsu-kakade-liang2012}, etc. In
this work, we provide a spectral algorithm for a discriminative model,
a mixture of linear regressions.

@@

Our approach uses regression to recover the moments of the data from the
scalar observable output variable. Once we recover the second and third
moments of the regression coefficients, we use a slight modification of
the method outlined in \citet{anandkumar-hsu-kakade2012}.

@@

In \autoref{sec:model}, we formally define the mixture of linear
regressions model and discuss when it is identifiable. We describe our
algorithm and provide some theoretical results in \autoref{sec:algo}. We
present the results of our evaluations in \autoref{sec:evaluation}.
Finally, we discuss the merits and demerits of spectral algorithms in
discriminative models and conclude in \autoref{sec:discussion}. The
details of some proofs can be found in \autoref{sec:proofs}.

>>>>

Local optima are a common problem plaguing the learning of parameters in
latent variable models. Recently, there has been an interest in spectral
algorithms that provide statistically consistent estimators, i.e. given
sufficient data they are guaranteed to converge to the global optimum,
given that the model is identifiable. Furthermore, these algorithms have
polynomial sample and computational complexities for several such
models, e.g.  hidden Markov models \cite{AnandkumarHsuKakade2012},
probabilistic context free grammars \cite{HsuKakadeLiang2012}, etc. In
this work, we provide a spectral algorithm for a discriminative model,
the mixture of linear regressions.

@@

Our approach uses regression to recover the moments of the data from the
scalar observable output variable. Once we recover the second and third
moments of the regression coefficients, we use a slight modification of
the method outlined in \citet{AnandkumarHsuKakade2012}.

@@

In \sectionref{sec:model}, we formally define the mixture of linear
regressions model and discuss when it is identifiable. We describe our
algorithm and provide some theoretical results in \sectionref{sec:algo}. We
present the results of our evaluations in \sectionref{sec:evaluation}.
Finally, we discuss the merits and demerits of spectral algorithms in
discriminative models and conclude in \sectionref{sec:discussion}. The
details of some proofs can be found in \sectionref{sec:proofs}.
